Inattentive responding can induce spurious associations between task behaviour and symptom measures

### 2020-11-01 manuscripts/main.tex
updated sanity checks

>>>>

\begin{table}[t]
\centering
\setlength{\tabcolsep}{6pt}
\begin{tabular}{lcccccc}
\toprule
& \multicolumn{2}{c}{Avg. Total Score} & \multicolumn{2}{c}{Fraction} & \multicolumn{2}{c}{Cronbach's $\alpha$} \\
\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7}
 Subscale & No Fail & Any Fail & No Fail & Any Fail & No Fail & Any Fail \\
\midrule
7-up    &  3.87 &  10.15 &  0.04 &  0.45 &  0.84 &  0.84 \\
7-down   &  4.75 &  10.68 &  0.09 &  0.46 &  0.94 &  0.88 \\
GAD7  &  4.86 &   9.73 &  0.17 &  0.56 &  0.92 &  0.87 \\
PSWQ  &  4.78 &   6.74 &  0.07 &   0.08 &  0.93 &  0.81 \\
BIS   &  7.74 &   7.92 &   - &   - &  0.83 &  0.62 \\
BAS-R &  6.38 &   7.38 &   - &   - &  0.71 &  0.60 \\
BAS-D &  9.35 &   8.79 &   - &   - &  0.86 &  0.69 \\
SHAPS &  8.02 &  10.85 &   0.15 &   0.29 &  0.90 &  0.81 \\
\bottomrule
\end{tabular}
\caption{}
\label{tab:screening}
\end{table}
